\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{fullpage}
\begin{document}
\pagestyle{empty}
\hyphenpenalty=10000

\begin{center}

	\textsf{
		\textbf{
			\LARGE Paper Code : 21312\\
			\normalsize F-412\\
			B.C.A. (IIIrd Semester)\\
			Examination, 2019-20\\
			(New Course)\\
			\small{COMPUTER ORGANISATION\\}
		}
		Paper-BCA-302
	}

	\begin{minipage}{0.49\linewidth}
		\raggedright\footnotesize Time : 3 Hours ]
	\end{minipage}
	\begin{minipage}{0.49\linewidth}
		\raggedleft\footnotesize [ Maximum Marks : 70
	\end{minipage}

\end{center}

\rule{0.9\linewidth}{0.1mm}

\begin{description}
	\item[\textit{Note }:-] Attempt any \textit{five} questions. All questions carry equal marks.
\end{description}

\begin{enumerate}

	\item[1.]
	\begin{enumerate}
		\item Describe in detail constructing of Arithmetic Logic Unit (ALU).
		\item What do you mean by Floating point arithmetic ? Explain it with an example.
	\end{enumerate}

	\item[2.]
	\begin{enumerate}
		\item Convert the following numbers accordingly :
			\begin{enumerate}
				\item $(10111010)_2 = (?)_{10}$
				\item $(\textnormal{ABD}45)_{16} = (?)_8$
				\item $(10011010)_2 = (?)_{\textnormal{Gray}}$
				\item $(128)_{10} = (?)_2$
				\item $(167)_9 = (?)_2$
			\end{enumerate}
		\item How many types of instruction format ? Describe the all field of instruction format with an example.
	\end{enumerate}

	\item[3.] Describe the following addressing mode with an example :
	\begin{enumerate}
		\item Implied mode
		\item Immediate mode
		\item Register indirect mode
		\item Autoincrement or autodecrement mode
		\item Direct addressing mode
		\item Indirect addressing mode
	\end{enumerate}

	\item[4.] Explain the following :
	\begin{enumerate}
		\item Micro-operation
		\item Micro-instruction
		\item Micro-program
		\item Micro-code
	\end{enumerate}

	\item[5.]
	\begin{enumerate}
		\item Differentiate between the following memory :
			\begin{enumerate}
				\item RAM and ROM
				\item PROM and EEPROM
			\end{enumerate}
		\item How many 256 $\times$ 8 RAM chips are needed to provide a memory capacity of 4096 bytes ?
	\end{enumerate}

	\item[6.]
	\begin{enumerate}
		\item Differentiate between segmented memory system and paged segment memory.
		\item Describe the characteristics of cache memory.
	\end{enumerate}

	\item[7.]
	\begin{enumerate}
		\item Describe the need of bus arbitration in system organizataion.
		\item Explain the architecture of DMA in detail.
	\end{enumerate}

	\item[8.] Write short notes on any \textit{four} of the following :
	\begin{enumerate}
		\item Logical operation
		\item Primary memory
		\item Static RAM
		\item High speed memory
		\item Reverse polish notation
		\item IEEE floating point notation
	\end{enumerate}

\end{enumerate}

\end{document}