\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{fullpage}
\begin{document}
\pagestyle{empty}
\hyphenpenalty=10000

\begin{center}

	\textsf{
		\textbf{
			\LARGE Paper Code : 21314\\
			\normalsize F-414\\
			B.C.A. (IIIrd Semester)\\
			Examination, 2019-20\\
			(New Course)\\
			\small{OBJECT ORIENTED USING C++\\}
		}
		Paper-BCA-304
	}

	\begin{minipage}{0.49\linewidth}
		\raggedright\footnotesize Time : 3 Hours ]
	\end{minipage}
	\begin{minipage}{0.49\linewidth}
		\raggedleft\footnotesize [ Maximum Marks : 70
	\end{minipage}

\end{center}

\rule{0.9\linewidth}{0.1mm}

\begin{description}
	\item[\textit{Note }:-] Attempt any \textit{five} questions. All questions carry equal marks.
\end{description}

\begin{enumerate}

	\item[1.]
	\begin{enumerate}
		\item Define OOP's concepts in detail. Write its application area.
		\item Define the various access specifiers used in class and their purpose also.
	\end{enumerate}

	\item[2.]
	\begin{enumerate}
		\item What do you mean by classification and composition ?
		\item How many types a function can be define in a class ? Explain each with in one program.
	\end{enumerate}

	\item[3.]
	\begin{enumerate}
		\item What is the difference between Do-while and While loop ? Explain each with a program.
		\item What is the difference between Call by Value and Call by Reference ? Explain each with program.
	\end{enumerate}

	\item[4.]
	\begin{enumerate}
		\item What is constructor ? Write a program for constructor overloading.
		\item Write a program to find the factorial of a given number by using recursion.
	\end{enumerate}

	\item[5.]
	\begin{enumerate}
		\item Explain friend function. Give \textit{five} characteristics of friend function. Why friend function is not defined with scope resolution operator ?
		\item Write a program of prime number by using friend function.
	\end{enumerate}

	\item[6.] What is operator overloading ? Limitation of member function in binary Operator overloading. Write a program to overload a `-' operator by using friend function.

	\item[7.] Explain the term inheritance and its types in detail with proper syntax.

	\item[8.] Write short notes on the following :
	\begin{enumerate}
		\item Association
		\item Scope resolution operator
		\item Function overloading
		\item Operators
	\end{enumerate}

\end{enumerate}

\end{document}