\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{fullpage}
\begin{document}
\pagestyle{empty}
\hyphenpenalty=10000

\begin{center}

	\textsf{
		\textbf{
			\LARGE Paper Code : 21313\\
			\normalsize F-413\\
			B.C.A. (IIIrd Semester)\\
			Examination, 2019-20\\
			(New Course)\\
			\small{DATA STRUCTURES USING C\\}
		}
		Paper-BCA-303-N
	}

	\begin{minipage}{0.49\linewidth}
		\raggedright\footnotesize Time : 3 Hours ]
	\end{minipage}
	\begin{minipage}{0.49\linewidth}
		\raggedleft\footnotesize [ Maximum Marks : 70
	\end{minipage}

\end{center}

\rule{0.9\linewidth}{0.1mm}

\begin{description}
	\item[\textit{Note }:-] Attempt any \textit{five} questions. All questions carry equal marks.
\end{description}

\begin{enumerate}

	\item[1.]
	\begin{enumerate}
		\item What is data structure ? Discuss the different types of data structures with features.
		\item What is Stack ? Write an Algorithm to implement stack using linked list.
	\end{enumerate}

	\item[2.]
	\begin{enumerate}
		\item Explain why circular queue is better than linear queue.
		\item Write a function to delete a node from beginning of double linked list.
	\end{enumerate}

	\item[3.]
	\begin{enumerate}
		\item Write a recursive function to count number of nodes in tree.
		\item Convert the following infix expression into postfix expression.
			\begin{center}
				(A + B - C * D)/H
			\end{center}
	\end{enumerate}

	\item[4.]
	\begin{enumerate}
		\item Compare Selection sort and Merge sort.
		\item Define Hashing. Discuss any \textit{two} hashing methods with example.
	\end{enumerate}

	\item[5.]
	\begin{enumerate}
		\item Explain height balance tree and AVL tree with suitable example.
		\item Explain the concept of asymptotic notations.
	\end{enumerate}

	\item[6.]
	\begin{enumerate}
		\item Construct a binary tree for the following inorder traversal :
			\begin{center}
				B G H D A E C I J K F J
			\end{center}
		\item Explain Overflow and Underflow condition on stack.
	\end{enumerate}

	\item[7.]
	\begin{enumerate}
		\item What is BST ? Explain algorithm for insertion in BST.
		\item What is Graphs ? Explain Multigraphs and Directed Graphs.
	\end{enumerate}

	\item[8.] Explain any \textit{four} of the following :
	\begin{enumerate}
		\item D-queue and Priority queue
		\item Doubly Linked list
		\item Tower of Hanoi problem with \textit{three} disc
		\item Sequential and Binary Search
		\item Sparse Matrix.
	\end{enumerate}

\end{enumerate}

\end{document}