\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{fullpage}
\begin{document}
\pagestyle{empty}
\hyphenpenalty=10000

\begin{center}

	\textsf{
		\textbf{
			\LARGE Paper Code : 21315\\
			\normalsize F-415\\
			B.C.A. (IIIrd Semester)\\
			Examination, 2019-20\\
			(New Course)\\
			\small{ORGANISATIONAL BEHAVIOUR\\}
		}
		Paper-BCA-305-N
	}

	\begin{minipage}{0.49\linewidth}
		\raggedright\footnotesize Time : 3 Hours ]
	\end{minipage}
	\begin{minipage}{0.49\linewidth}
		\raggedleft\footnotesize [ Maximum Marks : 70
	\end{minipage}

\end{center}

\rule{0.9\linewidth}{0.1mm}

\begin{description}
	\item[\textit{Note }:-] Attempt any \textit{five} questions. All questions carry equal marks.
\end{description}

\begin{enumerate}

	\item[1.] ``Behavioural Science is scientific study of human behaviour.'' Comment.

	\item[2.] Define perception. What are the various factors affecting perceptual selectivity and perceptual distortion.

	\item[3.] Define learning. What is the difference between the classical conditioning and operant conditioning theories of learning ?

	\item[4.] Discuss the concept of managerial grid created by R.R. Blake and J.S. Monton. What are managerial applications of it ?

	\item[5.] Differentiate between group, team, and organisation. What is group cohesiveness ? Discuss the various factors affecting it.

	\item[6.] Discuss the various types of organizational conflict. Distinguish between intra-individual and inter-individual conflict.

	\item[7.] Differentiate between authority and power. Explain dysfunctional uses of power and politics.

	\item[8.] Discuss the various outcomes which arise out because of the non-satisfaction of needs.

	\item[9.] Differentiate between the following :
	\begin{enumerate}
		\item Formal and informal group
		\item Programmed and non-programmed decisions
		\item Power and Politics
		\item Values and attitude
		\end{enumerate} 

	\item[10.] Write short notes on any \textit{two} of the following :
	\begin{enumerate}
		\item Models of OB
		\item Stages of group development
		\item Trait theory of leadership
		\item Conflict resolution strategy
	\end{enumerate}

\end{enumerate}

\end{document}